---
title: "Practical Machine Learning Course Project"
author: "Vaso Liakouli"
date: "2023-06-08"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Synopsis
This analysis reviews data related to how well individuals have performed 
specific activities in the gym.
We will apply different methods in order to be able to predict the "classe" 
attribute of the data set that indicates the manner the exercise was executed.


## Data Processing
For the data processing, we will download the data, in case they are not already 
available under our working directory.  
 

```{r cache = TRUE, echo = FALSE}
## Include required libraries
library(dplyr)

## Set working directory


## Check if the file already exists under the working directory, if not, download it.
training_file <- "pml-training.csv"
testing_file  <- "pml-testing.csv"

if (!file.exists(training_file)) {
  
  fileurl_train  <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
  destfile_train <- "pml-training.csv"
  download.file(fileurl_train,destfile_train)
}


if (!file.exists(testing_file)) {
  
  fileurl_test  <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
  destfile_test <- "pml-testing.csv"
  download.file(fileurl_test,destfile_test)
}

## Read the CSV file
data_train <- read.csv("pml-training.csv")
data_test  <- read.csv("pml-testing.csv")
```



## Appendix
Put graphs here 
 
